The Emotional Coherence Controversy: Evidence from Human and Automatic Expression Recognition

### 2019-04-23 ACII_2019_paper/ACII_2019_paper.Rmd
typo

## A. The Behaviorist Approach
Based on the behaviorist approach initiated by Darwin in *The Expression of the Emotions in Man and Animals* [@darwin1872expression], facial expressions are conceived as a genuine displays of an individual's inner emotional state. This hypothesis is used as a basis for the Basic Emotion Theory (BET) which states that a set of six emotions are universally displayed and are genetically hardwired not only in humans [@ekman1992argument] but also in different animal species [@de2019mama]. According to this view, *“when emotions are aroused by perception of a social event, a set of central commands produce patterned emotion-specific changes in multiple systems, including […] facial expressions.”* [@ekman2007directed, 49]. To respond to criticisms, several amendments have been made to the BET, increasing the number of basic emotions from six to seven [@ekman1988universality] as well as adding the concept of “display rules” to explain cultural differences in the management of facial expressions [@ekman1987universals].

>>>>

## A. The Behaviorist Approach
Based on the behaviorist approach initiated by Darwin in *The Expression of the Emotions in Man and Animals* [@darwin1872expression], facial expressions are conceived as a genuine displays of an individual's inner emotional state. This hypothesis is used as a basis for the Basic Emotion Theory which states that a set of six emotions are universally displayed and are genetically hardwired not only in humans [@ekman1992argument] but also in different animal species [@de2019mama]. According to the view of the Basic Emotion Theory, *“when emotions are aroused by perception of a social event, a set of central commands produce patterned emotion-specific changes in multiple systems, including […] facial expressions.”* [@ekman2007directed, 49]. To respond to criticisms, several amendments have been made to the Basic Emotion Theory, increasing the number of basic emotions from six to seven [@ekman1988universality] as well as adding the concept of “display rules” to explain cultural differences in the management of facial expressions [@ekman1987universals].

### 2019-04-23 ACII_2019_paper/ACII_2019_paper.tex
typo

Based on the behaviorist approach initiated by Darwin in \emph{The
Expression of the Emotions in Man and Animals} {[}2{]}, facial
expressions are conceived as a genuine displays of an individual's inner
emotional state. This hypothesis is used as a basis for the Basic
Emotion Theory (BET) which states that a set of six emotions are
universally displayed and are genetically hardwired not only in humans
{[}3{]} but also in different animal species {[}4{]}. According to this
view, \emph{``when emotions are aroused by perception of a social event,
a set of central commands produce patterned emotion-specific changes in
multiple systems, including {[}\ldots{}{]} facial expressions.''} {[}5,
p. 49{]}. To respond to criticisms, several amendments have been made to
the BET, increasing the number of basic emotions from six to seven
{[}6{]} as well as adding the concept of ``display rules'' to explain
cultural differences in the management of facial expressions {[}7{]}.

>>>>

Based on the behaviorist approach initiated by Darwin in \emph{The
Expression of the Emotions in Man and Animals} {[}2{]}, facial
expressions are conceived as a genuine displays of an individual's inner
emotional state. This hypothesis is used as a basis for the Basic
Emotion Theory which states that a set of six emotions are universally
displayed and are genetically hardwired not only in humans {[}3{]} but
also in different animal species {[}4{]}. According to the view of the
Basic Emotion Theory, \emph{``when emotions are aroused by perception of
a social event, a set of central commands produce patterned
emotion-specific changes in multiple systems, including {[}\ldots{}{]}
facial expressions.''} {[}5, p. 49{]}. To respond to criticisms, several
amendments have been made to the Basic Emotion Theory, increasing the
number of basic emotions from six to seven {[}6{]} as well as adding the
concept of ``display rules'' to explain cultural differences in the
management of facial expressions {[}7{]}.
